\section{Schedule} \label{sec:schedule}
A schedule is a set of instruction of when each payload is suppose to start and end, furthermore we define a valid schedule to obey the following criteria (i) payloads should only run when dependencies are uphold (ii) payloads with windows should only run during their windows (iii) during the schedule battery levels may not go below the specified threshold at any point during the entire schedule.

Since a schedule has a concept of time it is relevant to discuss the type of real-time category the schedule are in.
Three categories exist within real-time systems, hard, firm, and soft. Hard defines that if a payload exceed its deadline it will have catastrophic consequence or system failure. Firm will have no critical consequence but the data gathered by the payload will be of no value if it go over its deadline. Lastly soft will diminish is results the longer it misses its deadline\cite{real_time_computing}. 

Our schedule is either firm or soft depending on how we tend to interoperate the above definition. Let say we need to do two payloads that each transmit data to earth and give some unforeseen consequences only one of the payload are able to be executed within time, that leaves the nanosatellite with some data that it would have otherwise send. So given this the nanosatellite could either save the old data and generate the remaining data to be able to send two payloads at the next window. This can be categories as soft real-time because the data is still relevant when the next window is met. The other case is to erase the old data and generate entirely new data. Given that we are unable to adjust when he schedule is running on the nanosatellite the last case is much more likely, this would result in the old data being of zero value and is therefore categorized as firm real-time.  

The schedule will need to be robust, meaning being capable of handling errors, such as; the satellite will sometimes have to restart at unforeseen times, or maybe the moon blocks the sun and the battery would therefore not recharge as much as expected. This may cause the satellite to fall behind schedule and would in some way need to compensate for this.

% Weakly hard
% http://ieeexplore.ieee.org/stamp/stamp.jsp?arnumber=919277
% Reasoning: We can do a lot of things whenever, but have to send data in surtain windows, and must receive new schedules at some point